Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-03-05 paper.tex
correcciones ortograficas minimas

Besides, for a given $v_d>2\,$m/s, the overlap increases as the $k_n$ value
decreases.  This can be explained by considering the bulk at a (quasi)
equilibrium situation.  The social and compression forces counterbalance the
desired force. Thus, for any fixed $v_d$, the product $k_n \times
(R_{ij}-r_{ij})$ remains (almost) fixed. Any decrease in $k_n$ allows a more
significant intrusion. This (partially) supports the argument that the sliding
friction should weaken for stiffer pedestrians (say increasing $k_n$ values). \\

@@

Figs. \ref{flow_density} show the pedestrian flow as a function of the global
density (fundamental diagram). Fig.~\ref{flow_density_no_body_force} corresponds
to $\mathcal{K}_c=$ 0 (this is \textit{i.e.} $k_n=0$) while
Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68
corresponding to the original SFM with $k_n=1.2\,$E5. Each curve represents
different friction values (see the caption for details).\\

According to the empirical measurements at Jamaraat, the flow slows down for
high enough densities due to jamming. Notice that the original SFM
(corresponding to $\mathcal{K}=$137) does not produce the expected slowing down
for null body force ($\mathcal{K}_c=$0). However, when the body force is present
(the original SFM) an ``U'' shape behavior occurs for densities above 5
p$^{-2}$.\\

@@

A further increment of $\mathcal{K}$ to $\mathcal{K}=$1371 (ten times the 
original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at 
very high densities. This occurs on either $\mathcal{K}_c=$ 0 and 
$\mathcal{K}_c = $ 68.\\

@@

Having adopted as fundamental philosophy of work that the parameters of the SFM
should be properly determined by requiring that the model reproduces
well established experimental data, we explored the effect on the pedestrians
dynamics of the (sometimes neglected) body force in the framework of the SFM. We
showed that the stiffness coefficient ($k_n$) has a significant impact on the
evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking
along a straight corridor.\\

>>>>

Besides, for a given $v_d>2\,$m/s, the overlap increases as the $k_n$ value
decreases.  This can be explained by considering the bulk at a (quasi)
equilibrium situation.  The social and compression forces counterbalance the
desired force. Thus, for any fixed $v_d$, the product $k_n \times
(R_{ij}-r_{ij})$ remains (almost) fixed. Any decrease in $k_n$ allows a more
significant intrusion. This (partially) supports the argument that the sliding
friction should weaken for stiffer pedestrians (say increasing $k_n$ values).\\

@@

Figs. \ref{flow_density} show the pedestrian flow as a function of the global
density (fundamental diagram). Fig.~\ref{flow_density_no_body_force} corresponds
to $\mathcal{K}_c=$ 0 (this is \textit{i.e.} $k_n=0$) while
Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$ 68
corresponding to the original SFM with $k_n=1.2\,$E5. Each curve represents
different friction values (see the caption for details).\\

According to the empirical measurements at Jamaraat, the flow slows down for
high enough densities due to jamming. Notice that the original SFM
(corresponding to $\mathcal{K}=$ 137) does not produce the expected slowing down
for null body force ($\mathcal{K}_c=$ 0). However, when the body force is
present (the original SFM) an ``U'' shape behavior occurs for densities above 5
p$^{-2}$.\\

@@

A further increment of $\mathcal{K}$ to $\mathcal{K}=$ 1371 (ten times the 
original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at 
very high densities. This occurs on either $\mathcal{K}_c=$ 0 and 
$\mathcal{K}_c = $ 68.\\

@@

Having adopted as fundamental philosophy of work that the parameters of the SFM
should be properly determined by requiring that the model reproduces
well established experimental data; we explored the effect on the pedestrians
dynamics of the (sometimes neglected) body force in the framework of the SFM. We
showed that the stiffness coefficient ($k_n$) has a significant impact on the
evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking
along a straight corridor.\\
